A Way Forward in Parallelising Dynamic Languages

### 2014-05-05 talk/icooolps2014/position-paper.tex
~\cite

We believe that further work to reduce the overhead of STM is
very worthwhile. In fact, considering some analogies that have been
drawn between garbage collection and transactional memory \cite{dan07},
we believe that it is worthwhile to focus the STM research more
specifically on the context shown in this paper --- for use in
implementations of high-level languages, rather than as a tool
directly used by the programmer.

>>>>

We believe that further work to reduce the overhead of STM is
very worthwhile. In fact, considering some analogies that have been
drawn between garbage collection and transactional memory~\cite{dan07},
we believe that it is worthwhile to focus the STM research more
specifically on the context shown in this paper --- for use in
implementations of high-level languages, rather than as a tool
directly used by the programmer.
